---
title: "homelocator" 
date: "Last compiled on `r format(Sys.time(), '%d %b, %Y')`"
author: Qingqing Chen, Ate Poorthuis
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{homelocator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::load_all(".")
library(homelocator)
```

# Introduction

<p align="justify">The `homelocator` library is designed for identifying meaningful locations for users based on the spatial and temporal features contained within the mobility data, such as social media data, mobile phone data and so on.</p>

<p align="justify">The main objective for developing this package is to provide a consistent framework and interface for the adoption of different approaches so that researchers are able to write structured, algorithmic 'recipes' to identify the meaningful locations according to their research requirement and able to achieve an apples-to-apples comparison across the approaches.</p>

<p align="justify">We hope that through packages and libraries like the one presented here, future work that relies on the inference of meaningful locations becomes less ‘custom’ (with each researcher writing their own algorithm) but instead will use common, comparable algorithms in order to increase transparency and reproducibility in the field.</p>


```{r echo=FALSE, results='hide', message=F}
# Load other needed libraries
library(tidyverse)
library(emo)
library(lubridate)
library(here)
```

# Test Data

To explore the basic data manipulation functions of `homelocator`, we'll use a `test_sample` dataset. 

```{r}
# load data
test_sample <- readRDS(here("data/new_test_sample.rds"))

# show test sample 
test_sample %>% head(3)
```

<span style="color:red">*Note:*</span> *if you use your own dataset, please make sure that you have coverted the data timestamp to your local time zone!*

# Usage

## Functions

### Validate input dataset 

The `validate_dataset()` function in `validate_datset.R` script makes sure your input dataset contains all three necessary variables: user, locaiton and timestamp. There are 4 augments in this function: 

  - `user`: name of column that holds unique identifier for each user 
  - `timestamp`: name of column that holds specific timestamp for each data point and it should be `POSIXct`
  - `location`: name of column that holds unique identifier for each location
  - `keep_other_vars`: option to keep or remove other variables of the input dataset. The default is `FALSE`


```{r}
df_validated <- validate_dataset(test_sample, user = "u_id", timestamp = "created_at", 
                                 location = "grid_id", keep_other_vars = FALSE)

# show result 
df_validated %>% head(3)
```


### Nest and Unnest 

The `nest_verbose()` and `unnest_verbose()` functions in `nest.R` script work in the same way as  [nest](https://www.rdocumentation.org/packages/tidyr/versions/0.8.3/topics/nest) and [unnest](https://www.rdocumentation.org/packages/tidyr/versions/0.8.3/topics/unnest) functions in [tidyverse](https://github.com/tidyverse/tidyverse) but with extra information of elapsed runing time. 
  
  - `df`: a dataframe
  - `...`: for `nest_verbose()` refers to selected columns to nest and for `unnest_verbose()` refers to list-column to unnest.
 

```{r}
# nest data
df_nested <- nest_verbose(df_validated, c("created_at", "grid_id"))

# show result 
df_nested %>% head(3)

# show result 
df_nested$data[[1]] %>% head(3)

# unnest data
df_unnested <- unnest_verbose(df_nested, data)

# show result 
df_unnested %>% head(3)
```


### Double nest and Double unnest

The `nest_double_nest()` and `unnest_double_nested()` functions in `nest.R` script work in the similar way as `nest_verbose()` and `unnest_verbose()` functions but they apply to nested dataframe. In another words, they map `nest` and `unnest` function to each element of a list.
  
  - `df`: a nested dataframe
  - `...`: for `nest_double_nest()` refers to selected columns to nest and for `unnest_double_nested()` refers to list-column to unnest.
 

```{r}
# double nest data
df_double_nested <- nest_nested(df_nested %>% head(100), c("created_at"))

# show result 
df_double_nested %>% head(3)

# show result 
df_double_nested$data[[3]] %>% head(3)

df_double_nested$data[[3]]$data[[2]] %>% head(3)

# unnest nested data 
df_double_unnested <- df_double_nested %>% 
  head(100) %>%  ## take first 100 rows for example
  unnest_double_nested(., data) 

# show result 
df_double_unnested %>% head(3)
```


### Enrich timestamp 

The `enrich_timestamp()` in `enrich_timestamp.R` script allows to derive new variables from timestamp column in each element of a list including: year, month, day, day of the week and hour of the day. The day of the week is a decimal number where 1 means Sunday and 7 means Saturday. 

  - `df`: a nested dataframe
  - `timestamp`: name of column that holds specific timestamp for each data point and it should be `POSIXct`
  - `tz`: a character string containing the time zone to convert to and it should be recognized in R. The default `tz` is set to `Asia/Singapore`.

```{r}
# create new varialbes from "created_at" timestamp column 
df_enriched <- enrich_timestamp(df_nested, timestamp = "created_at", tz = "Asia/Singapore")

# show result 
df_enriched$data[[3]] %>% head(3)
```



### Summarize in nested and double nested dataframe 

The `summarise_nested()` funciton in `summarise.R` script allows to aggregate multiple values to a single value of exisiting table by specified summary function for each element in a list.  `summarise_double_nested()` function create a new list-column inside existing list-column first and then aggregate multiple values in created list-column to a single value by name-value paired summary functions. 

  - `df`: a nested dataframe 
  - `nest_cols`: a selection of columns to nest in existing list-column
  - `...`: name-value pairs of summary functions 

```{r}
# summarize in nested dataframe 
df_summarize_nested <- summarise_nested(df_enriched, 
                                        n_tweets = n(),
                                        n_locs = n_distinct(grid_id))

# show result 
df_summarize_nested %>% head(3)

# summarize in double nested dataframe (take first 100 users for example)
df_summarize_double_nested <- summarise_double_nested(df_enriched %>% head(100), 
                                                      nest_cols = c("created_at", "ymd"), 
                                                      n_tweets = n(), n_days = n_distinct(ymd))

# show result 
df_summarize_double_nested[3, ]
df_summarize_double_nested[3, ]$data[[1]] %>% head(3)
```


### Remove active users 

The `remove_top_users()` funciton in `remove_top_users.R` script allows to remove top `N` percent of active users based on the total number of data points of users. Although the majority of users are real people, some users are accounts that are run by algorithms or 'bots', whereas others can be considered as spam accounts. So you can choose to remove certain top `N` percent of active users. 

  - `df`: a dataframe with columns of user id, and data point counts 
  - `user`: name of column that holds unique identifier for each user
  - `counts`: name of column that holds the data points frequency for each user         
  - `topNpct_user`: a decimal number that represent the certain percentage of users to remove

```{r}
# remove top 1% active users
df_removed_active_users <- remove_top_users(df_summarize_nested, user = "u_id", 
                                            counts = "n_tweets", topNpct_user = 1) 

# show result 
df_removed_active_users %>% head(3)
```


### Filter 

The `filter_verbose()` function in `filter.R` script works in the same way as [filter](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8/topics/filter) function in [tidyverse](https://github.com/tidyverse/tidyverse) but with information of user numbers in the dataset. And the `filter_nested()` function works in the similar way as `filter_verbose()` but is applied in the list-column. 

  - `df`: a dataframe with columns of user id, and variables that your are going to apply the filter function. If the column not in the dataset, you need to add that column before you apply the filter
  - `user`: name of column that holds unique identifier for each user 
  - `...`: Logical predicates defined in terms of the variables in df. Only rows match conditions are kept.

```{r}
# filter users with less than 10 tweets sent at less than 10 places 
df_filtered <- filter_verbose(df_removed_active_users, user = "u_id", 
                              n_tweets > 10 & n_locs > 10)

# show result 
df_filtered %>% head(3)

# filter tweets that sent on weekends and during daytime (8am to 6pm)
df_filter_nested <- filter_nested(df_filtered, user = "u_id", 
                                  !wday %in% c(1, 7), # 1 means Sunday and 7 means Saturday
                                  !hour %in% seq(8, 18, 1)) 

# show result 
df_filter_nested %>% head(3)

df_filter_nested$data[[1]] %>% head(3)
```


### Mutate 

The `mutate_verbose()` function in `filter.R` script works in the same way as [mutate](https://www.rdocumentation.org/packages/dplyr/versions/0.5.0/topics/mutate) function in [tidyverse](https://github.com/tidyverse/tidyverse) but with information of function running time. 

  - `df`: a dataframe 
  - `...`: name-value pairs of expressions

Function `mutate_nested()` works in the similar way as `mutate_verbose()` but it add new variables inside the list-column. 

  - `df`: a nested dataframe 
  - `...`: name-value pairs of expressions
  
  
```{r}
## let's use pre-discussed functions to filter some users first 
colnmaes_data <- df_filtered$data[[1]] %>% names()
colnmaes_to_nest <- colnmaes_data[-which(colnmaes_data == "grid_id")] 

df_cleaned <- df_filtered %>% 
  summarise_double_nested(., nest_cols = colnmaes_to_nest,
                          n_tweets_loc = n(), # number of tweets sent at each location
                          n_hrs_loc = n_distinct(hour), # number of unique hours of sent tweets 
                          n_days_loc = n_distinct(ymd), # number of unique days of sent tweets 
                          period_loc = as.numeric(max(created_at) - min(created_at), "days")) %>% # period of tweeting 
  unnest_verbose(data) %>% 
  filter_verbose(., user = "u_id",
                 n_tweets_loc > 10 & n_hrs_loc > 10 & n_days_loc > 10 & period_loc > 10) 
  
# show cleaned dataset 
df_cleaned %>% head(3)

# ok, then let's apply the mutate_nested function to add four new variables: wd_or_wk, time_numeric, rest_or_work, wk.am_or_wk.pm
df_expanded <- df_cleaned %>% 
  mutate_nested(wd_or_wk = if_else(wday %in% c(1,7), "weekend", "weekday"),
                time_numeric = lubridate::hour(created_at) + lubridate::minute(created_at) / 60 + lubridate::second(created_at) / 3600, 
                rest_or_work = if_else(time_numeric >= 9 & time_numeric <= 18, "work", "rest"), 
                wk.am_or_wk.pm = if_else(time_numeric >= 6 & time_numeric <= 12 & wd_or_wk == "weekend", "weekend_am", "weekend_pm")) 

# show result 
df_expanded %>% head(3)
```

The function `prop_factor_nested()` allows you to calculate the proportion of categories for a variable inside the list-column and convert each categories to a new variable adding to the dataframe. 

  - `df`: a nested dataframe 
  - `var`: name of column to calculate inside the list-column
  

```{r}
# calculate proportion of categories for four variables: wd_or_wk, rest_or_work, wk.am_or_wk.pm
df_expanded <- df_expanded %>% 
  prop_factor_nested(wd_or_wk, rest_or_work, wk.am_or_wk.pm) 

# show result 
df_expanded %>% head(3)
```


### Score 

The `score_nested()` function in `score.R` script allows you to give a weighted value for a varialbe in a nested dataframe. 

  - `df`: a nested dataframe by user 
  - `user`: name of column that holds unique identifier for each user
  - `location`: name of column that holds unique identifier for each location
  - `keep_ori_vars`: option to keep or drop original varialbes 
  - `...`: name-value pairs of expression 

The `score_summary()` function summarises all scored columns and return one single value per row. 
  
  - `df`: a dataframe 
  - `user`: name of column that holds unique identifier for each user
  - `location`: name of column that holds unique identifier for each location
  - `...`: name of scored columns 


```{r}
## let's add two more variables before we do the scoring 
df_expanded <- df_expanded %>% 
  summarise_nested(n_wdays_loc = n_distinct(wday),
                   n_months_loc = n_distinct(month))

df_expanded %>% head(3)

df_scored <- df_expanded %>% 
  score_nested(., user = "u_id", location = "grid_id", keep_original_vars = F,
               s_n_tweets_loc = 0.1 * (n_tweets_loc/max(n_tweets_loc)),
               s_n_hrs_loc = 0.1 * (n_hrs_loc/24), 
               s_n_days_loc = 0.1 * (n_days_loc/max(n_days_loc)),
               s_period_loc = 0.1 * (period_loc/max(period_loc)),
               s_n_wdays_loc = 0.1 * (n_wdays_loc/7),
               s_n_months_loc = 0.1 * (n_months_loc/12),
               s_weekend = 0.1 * (weekend),
               s_rest = 0.2 * (rest),
               s_wk_am = 0.1 * (weekend_am))

df_scored %>% head(3)
df_scored$data[[1]]

### we can replace the score function by mutate function 

df_scored_2 <- df_expanded %>% 
  nest_verbose(-u_id) %>% 
  mutate_nested(s_n_tweets_loc = 0.1 * (n_tweets_loc/max(n_tweets_loc)),
                s_n_hrs_loc = 0.1 * (n_hrs_loc/24), 
                s_n_days_loc = 0.1 * (n_days_loc/max(n_days_loc)),
                s_period_loc = 0.1 * (period_loc/max(period_loc)),
                s_n_wdays_loc = 0.1 * (n_wdays_loc/7),
                s_n_months_loc = 0.1 * (n_months_loc/12),
                s_weekend = 0.1 * (weekend),
                s_rest = 0.2 * (rest),
                s_wk_am = 0.1 * (weekend_am))

df_scored_2 %>% head(3)
df_scored_2$data[[1]]
```


```{r}
# sum varialbes score for each location 
df_score_summed <- df_scored %>% 
  score_summary(., user = "u_id", location = "grid_id", starts_with("s_"))

df_score_summed %>% head(3)
df_score_summed$data[[3]]
```


### Extract locations 

The `extract_location()` function in `extract_location.R` script allows you to sort the locations of each each user based on descending value of selected column, and return the top N location(s) for each user. The extracted locations thus be treated as the most possible home location of the user. 

  - `df`: a nested dataframe by user 
  - `user`: name of column that holds unique identifier for each user
  - `location`: name of column that holds unique identifier for each location
  - `show_n_loc`: a single number that decides the number of locations to be extracted 
  - `keep_score`: option to keep or remove columns with scored value 
  - `...`: name of column(s) that used to sort the locations 
  

```{r}
# extract homes for users based on score value (each user return 1 most possible home)
df_home <- df_score_summed %>% 
  extract_location(., user = "u_id", location = "grid_id", show_n_loc = 1, keep_score = F, score)

df_home %>% head(3)

# extract homes for users and keep scores of locations
df_home <- df_score_summed %>% 
  extract_location(., user = "u_id", location = "grid_id", show_n_loc = 1, keep_score = T, score)

df_home %>% head(3)
df_home$data[[3]]
```


### Spread 

The `spread_nested()` function in `spread.R` script works in the same way as [spread](https://www.rdocumentation.org/packages/tidyr/versions/0.8.3/topics/spread) function in [tidyverse](https://github.com/tidyverse/tidyverse) but for nested dataframe. It allows to spread a Key-Value Pair across multiple columns.

  - `df`: a nested dataframe 
  - `var_key`: column name or position
  - `var_value`: column name or position

```{r}
# let's add one timeframe variable first and calculate the number of data points at each timeframe
df_timeframe <- df_enriched %>% 
  mutate_nested(timeframe = if_else(hour >= 2 & hour < 8, "Rest", if_else(hour >= 8 & hour < 19, "Active", "Leisure")))

colnames_nested_data <- df_timeframe$data[[1]] %>% names()
colnmaes_to_nest <- colnames_nested_data[-which(colnames_nested_data %in% c("grid_id", "timeframe"))]

df_timeframe <- df_timeframe %>%
  head(20) %>% # take first 20 users as example
  summarise_double_nested(., nest_cols = colnmaes_to_nest, 
                            n_points_timeframe = n()) 
df_timeframe$data[[2]]

# spread timeframe in nested dataframe with key is timeframe and value is n_points_timeframe
df_timeframe_spreaded <- df_timeframe %>% 
    spread_nested(., key_var = "timeframe", value_var = "n_points_timeframe") 

df_timeframe_spreaded$data[[2]]
```


### Arrange 

The `arrange_nested()` function in `spread.R` script works in the same way as [arrange](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8/topics/arrange) function in [tidyverse](https://github.com/tidyverse/tidyverse) but for nested dataframe. It allows to sort rows by variables. 

  - `df`: a nested dataframe 
  - `...`: comma separated list of unquoted variable names
  
  

```{r}
df_enriched$data[[3]]  

df_arranged <- df_enriched %>% 
  arrange_nested(desc(hour)) # arrange the hour in descending order

df_arranged$data[[3]]
```

The `arrange_double_nested()` funtion works in the similar way as `arrange_nested()` function, but it applys to double nested dataframe. You need to choose the columns to nest inside a nested dataframe and then sort rows by selected column. 
  
    - `df`: a nested dataframe 
    - `nest_cols`: name of columns to nest in existing list-column
    - `...`: comma separated list of unquoted variable names 


```{r}
# get the name of columns to nest 
colnames_nested_data <- df_enriched$data[[1]] %>% names()
colnmaes_to_nest <- colnames_nested_data[-which(colnames_nested_data %in% c("grid_id"))]

df_double_arranged <- df_enriched %>% 
  head(20) %>% # take the first 20 users for example
  arrange_double_nested(., nest_cols = colnmaes_to_nest, 
                        desc(created_at)) # sort by time in descending order


# original third user
df_enriched[3, ]
# third user data points 
df_enriched$data[[3]]
# arranged third user
df_double_arranged[3, ]
# arranged time 
df_double_arranged$data[[3]]$data[[2]]
```



### Top N 

The `top_n_nested()` function in the `top_n.R` script works in the same way as [top_n](https://dplyr.tidyverse.org/reference/top_n.html) function in [tidyverse](https://github.com/tidyverse/tidyverse) but for nested dataframe. It allows to select the top entries in each group, ordered by wt.

```{r}
df_enriched$data[[2]]

## get the top 1 row based on hour 
df_top_1 <- df_enriched %>% 
  top_n_nested(., n = 1, wt = "hour")

df_top_1$data[[2]]
```



### Identify location(s) with embedded recipes 


To use the embedded recipes identifying the home location for users, you can use `identify_location()` function in `identify_location.R` script. 

  - `df`: a dataframe with columns for the user id, location, timestamp
  - `user`: name of column that holds unique identifier for each user
  - `timestamp`: name of timestamp column. Should be POSIXct
  - `location`: name of column that holds unique identifier for each location
  - `tz`: a character string containing the time zone to convert to and it should be recognized in R
  - `recipe`: embeded algorithms to identify the most possible home locations for users           
  - `show_n_loc`: number of potential homes to extract
  - `keep_score`: option to keep or remove calculated result/score per user per location


Current available recipes: 

- `recipe_HMLC`: 
  - Weighs data points across multiple time frames to ‘score’ potentially meaningful locations for each user 
- `recipe_FREQ`
  - Selects the most frequently 'visited' location assuming a user is active mainly around their home location. 
- `recipe_OSNA`: [Efstathiades et al.2015](https://www.researchgate.net/publication/279884727_Identification_of_Key_Locations_based_on_Online_Social_Network_Activity)
  - Finds the most 'popular' location during 'rest', 'active' and 'leisure time. Here we focus on 'rest' and 'leisure' time to find the most possible home location for each user. 
- `recipe_APDM`: [Ahas et al. 2010](https://www.researchgate.net/publication/233197970_Using_Mobile_Positioning_Data_to_Model_Locations_Meaningful_to_Users_of_Mobile_Phones)
  - Calculates the average and standard deviation of start time data points by a single user, in a single location. 


```{r eval = FALSE}
# recipe: homelocator -- HMLC
identify_location(test_sample, user = "u_id", timestamp = "created_at", 
                  location = "grid_id", show_n_loc = 1, recipe = "HMLC")

# recipe: Frequency -- FREQ
identify_location(test_sample, user = "u_id", timestamp = "created_at", 
                  location = "grid_id", show_n_loc = 1, recipe = "FREQ")

# recipe: Online Social Network Activity -- OSNA
identify_location(test_sample, user = "u_id", timestamp = "created_at", 
                  location = "grid_id", show_n_loc = 1, recipe = "OSNA")

# recipe: Online Social Network Activity -- APDM
## APDM recipe strictly returns the most likely home location
## It is important to load the neighbors table before you use the recipe!!
## example: st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
##          neighbors <- st_queen(df_sf) ===> convert result to dataframe 
df_neighbors <- readRDS(here::here("data/neighbors.rds"))
identify_location(test_sample, user = "u_id", timestamp = "created_at", 
                  location = "grid_id", recipe = "APDM", keep_score = F)
```
