---
title: "Quick start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Install package 

```{r eval=FALSE}
# Install development version from GitHub
install_github("spatialnetworkslab/homelocator")
```


## Load library

```{r setup}
# load homelocator package
library(homelocator)
```

```{r message=FALSE}
# load other packages needed for the analysis
library(tidyverse)
library(here)
```


## Load test data 
The test data includes 100 random users, and it can be used as an example to get started with `homelocator` package. 

```{r}
data("test_sample", package = "homelocator")
```

## Validate test sample 

The `validate_dataset()` function makes sure your input dataset contains all three necessary variables: user, location and timestamp. There are 4 arguments in this function: 

  - `user`: name of column that holds a unique identifier for each user.
  - `timestamp`: name of column that holds specific timestamp for each data point. This timestamp should be in `POSIXct` format.
  - `location`: name of column that holds a unique identifier for each location.
  - `keep_other_vars`: option to keep or remove any other variables of the input dataset. The default is `FALSE`.

_When validating the dataset, please specify the names of column for user, timestamp and location._

```{r}
validate_dataset(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", keep_other_vars = FALSE)
```

## Identify home locations with embedded recipes

### Recipe: HMLC

Weighs data points across multiple time frames to ‘score’ potentially meaningful locations for each user 

```{r eval = FALSE}
# recipe: homelocator -- HMLC
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "HMLC")
```

### Recipe: FREQ

Selects the most frequently 'visited' location assuming a user is active mainly around their home location. 
  
```{r eval = FALSE}
# recipe: Frequency -- FREQ
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "FREQ")
```

### Recipe: OSNA ([Efstathiades et al.2015](https://doi.org/10.1145/2808797.2808877)):

Finds the most 'popular' location during 'rest', 'active' and 'leisure time. Here we focus on 'rest' and 'leisure' time to find the most possible home location for each user. 

```{r eval = FALSE}
# recipe: Online Social Network Activity -- OSNA
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "OSNA")
```

### Recipe: APDM ([Ahas et al. 2010](https://doi.org/10.1080/10630731003597306))

Calculates the average and standard deviation of start time data points by a single user, in a single location. 

```{r eval = FALSE}
# recipe: Online Social Network Activity -- APDM
## APDM recipe strictly returns the most likely home location
## It is important to load the neighbors table before you use the recipe!!
## example: st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
##          neighbors <- st_queen(df_sf) ===> convert result to dataframe
data("df_neighbors", package = "homelocator")
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", recipe = "APDM", keep_score = F)
```

