---
title: "Quick start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Download homelocator open-sources 

Download `homelocator` open-sources from figshare at: https://figshare.com/s/ce7b8bcfd2e6b44a5568

## Install package 

Install the released version of `homelocator` as follows, where the **homelocator_0.1.0.tar.gz** is stored under `homelocator-open-sources/homelocator-package/`. 

```{r eval=FALSE}
remotes::install_local("~/Downloads/homelocator-open-sources/homelocator-package/homelocator_0.1.0.tar.gz", dependencies = T)
```


## Load library

```{r setup}
#load homelocator package 
library(homelocator)
```

```{r message=FALSE}
# load other packages needed for the analysis
library(tidyverse)
library(here)
```


## Load test sample 
The test sample includes 100 random users, and it will be used as the example to get quick started for using `homelocator` package. 

```{r}
data("test_sample", package = "homelocator")
```

## Validate test sample 

The `validate_dataset()` function in `validate_datset.R` script makes sure your input dataset contains all three necessary variables: user, location and timestamp. There are 4 arguments in this function: 

  - `user`: name of column that holds a unique identifier for each user.
  - `timestamp`: name of column that holds specific timestamp for each data point. This timestamp should be in `POSIXct` format.
  - `location`: name of column that holds a unique identifier for each location.
  - `keep_other_vars`: option to keep or remove any other variables of the input dataset. The default is `FALSE`.

_When validating the dataset, please specify the names of column for user, timestamp and location._

```{r}
validate_dataset(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", keep_other_vars = FALSE)
```

## Identify home locations with embeded recipes

### Recipe: HMLC

Weighs data points across multiple time frames to ‘score’ potentially meaningful locations for each user 

```{r eval = FALSE}
# recipe: homelocator -- HMLC
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "HMLC")
```

### Recipe: FREQ

Selects the most frequently 'visited' location assuming a user is active mainly around their home location. 
  
```{r eval = FALSE}
# recipe: Frequency -- FREQ
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "FREQ")
```

### Recipe: OSNA ([Efstathiades et al.2015](https://www.researchgate.net/publication/279884727_Identification_of_Key_Locations_based_on_Online_Social_Network_Activity)):

Finds the most 'popular' location during 'rest', 'active' and 'leisure time. Here we focus on 'rest' and 'leisure' time to find the most possible home location for each user. 

```{r eval = FALSE}
# recipe: Online Social Network Activity -- OSNA
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", show_n_loc = 1, recipe = "OSNA")
```

### Recipe: APDM ([Ahas et al. 2010](https://www.researchgate.net/publication/233197970_Using_Mobile_Positioning_Data_to_Model_Locations_Meaningful_to_Users_of_Mobile_Phones))

Calculates the average and standard deviation of start time data points by a single user, in a single location. 

```{r eval = FALSE}
# recipe: Online Social Network Activity -- APDM
## APDM recipe strictly returns the most likely home location
## It is important to load the neighbors table before you use the recipe!!
## example: st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
##          neighbors <- st_queen(df_sf) ===> convert result to dataframe 
data("df_neighbors", package = "homelocator")
identify_location(test_sample, user = "u_id", timestamp = "created_at", location = "grid_id", recipe = "APDM", keep_score = F)
```

