---
title: "Three method comparison"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4  
    number_sections: true  
    theme: united  
    highlight: tango  
    toc_float: true   
    code_folding: hide
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r library}
source("/Users/qingqing/Dropbox/SUTD/Ate/homelocator/vignettes/function_results_comparison.R")
```

## Load results of three methods 
- Hariton Efstathiades vs. Qingqing Chen
  - There are 9834 out of 10233 (96.10%) users have the same results
  - There are 399 out of 10233 (3.9%) users have the different results 
    - There are 169 (42.36%) users' different results are neighboring cells 
    - There are 230 (57.6%) users' different results are non-neighboring cells 
    
```{r load_census_data, message=FALSE, warning=FALSE}
options(tigris_use_cache = TRUE, tigris_class="sf")
census_api_key("2fcf1623c436882ad5e62a47280ab732d815e363")
st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
acs_ky <- tidycensus::get_acs(state = "KY", geography = "tract",
  variables = c(medincome = "B19013_001"),
  geometry = T, output = "wide", year = 2016)  %>%
  st_transform(., "+init=epsg:4326") %>%
  select(GEOID) %>%
  mutate(id = 1:nrow(.))
neighbors <- st_queen(acs_ky)
```

```{r load_sameResult_efs_qq, message=FALSE, warning=FALSE}
sameRes_efs_qq <- readr::read_csv(system.file("extdata", "sameRes_efs_qq.csv", package = "homelocator", mustWork = TRUE)) 
dim(sameRes_efs_qq)
knitr::kable(sameRes_efs_qq)
diffRes_efs_qq <- readr::read_csv(system.file("extdata", "diffRes_efs_qq.csv", package = "homelocator", mustWork = TRUE)) %>% mutate(GEOID = GEOID %>% as.character())
dim(diffRes_efs_qq)
knitr::kable(diffRes_efs_qq)
```

- Rein Ahas vs. Qingqing Chen
  - There are 9022 out of 9095 (99.20%) users have the same results
  - There are 73 out of 10233 (0.8%) users have the different results 
    - There are 51 (69.86%) users' different results are neighboring cells 
    - There are 22 (30.14%) users' different results are non-neighboring cells 
    
```{r load_results_ahas_qq, message=FALSE, warning=FALSE}
sameRes_ahas_qq <- readr::read_csv(system.file("extdata", "sameRes_ahas_qq.csv", package = "homelocator", mustWork = TRUE)) 
dim(sameRes_ahas_qq)
knitr::kable(sameRes_ahas_qq)
diffRes_ahas_qq <- readr::read_csv(system.file("extdata", "diffRes_ahas_qq.csv", package = "homelocator", mustWork = TRUE)) %>% mutate(GEOID = GEOID %>% as.character())
dim(diffRes_ahas_qq)
knitr::kable(diffRes_ahas_qq)
```

- Hariton Efstathiades vs. Rein Ahas
  - There are 9025 out of 9340 (96.63%) users have the same results
  - There are 315 out of 10233 (3.37%) users have the different results 
    - There are 213 (67.62%) users' different results are neighboring cells 
    - There are 102 (30.14%) users' different results are non-neighboring cells 
    
```{r load_results_ahas_efs, message=FALSE, warning=FALSE}
sameRes_ahas_efs <- readr::read_csv(system.file("extdata", "sameRes_ahas_efs.csv", package = "homelocator", mustWork = TRUE)) 
dim(sameRes_ahas_efs)
knitr::kable(sameRes_ahas_efs)
diffRes_ahas_efs <- readr::read_csv(system.file("extdata", "diffRes_ahas_efs.csv", package = "homelocator", mustWork = TRUE)) %>% mutate(GEOID = GEOID %>% as.character())
dim(diffRes_ahas_efs)
knitr::kable(diffRes_ahas_efs)
```

## Different results visualization
- Hariton Efstathiades VS. Qingqing Chen
  - Different results but are neighboring cells
  
```{r diff_efs_qq_neighbor, message=FALSE, warning=FALSE}
tmap_mode("view")
diff_users_efs_qq <- diffRes_efs_qq$u_id %>% unique()
# SELECT some users to show the results
plot1_users <- diff_users_efs_qq %>% 
  as_data_frame() %>% 
  mutate(id = 1:nrow(.)) %>% 
  filter(id %in% c(4, 6, 49, 38, 45, 48)) %>% 
  pull(value)
plot2_users <- diff_users_efs_qq %>% 
  as_data_frame() %>% 
  mutate(id = 1:nrow(.)) %>% 
  filter(id %in% c(1, 2, 3, 7, 13, 19)) %>% 
  pull(value)
view_diffUsers(diffRes_efs_qq, plot1_users)
```
    - Different results and are non-neighboring cells
    
```{r diff_efs_qq_non_neighbor, message=FALSE, warning=FALSE}
view_diffUsers(diffRes_efs_qq, plot2_users)
```

- Rein Ahas VS. Qingqing Chen
   - Different results but are neighboring cells
   
```{r ahas_qq_neighbor, message=FALSE, warning=FALSE}
diff_users_ahas_qq <- diffRes_ahas_qq$u_id %>% unique()
# SELECT some users to show the results
plot3_users <- diff_users_ahas_qq %>% 
  as_data_frame() %>% 
  mutate(id = 1:nrow(.)) %>% 
  filter(id %in% c(3, 13, 14, 17, 29, 30)) %>% 
  pull(value)
plot4_users <- diff_users_ahas_qq %>% 
  as_data_frame() %>% 
  mutate(id = 1:nrow(.)) %>% 
  filter(id %in% c(16, 19, 22, 23, 25, 36)) %>% 
  pull(value)
view_diffUsers(diffRes_ahas_qq, plot3_users)
```

    - Different results and are non-neighboring cells 
    
```{r ahas_qq_non_neighbor, message=FALSE, warning=FALSE}
view_diffUsers(diffRes_ahas_qq, plot4_users)
```













